Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-28 draft/ms_v5.tex
CModel magnitude

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Accuracy of the \cmodel{} magnitude}

    Fig \ref{fig:cmodel_mag} shows the photometric uncertainties of the
    \cmodel{} magnitudes in each band using the same format as Fig \ref{fig:psf_mag}.

    The overall performance of \cmodel{} photometry is reasonable down to 
    $i_{\mathrm{Input}}=25.2$ mag.
    Compared to the PSF photometry for stars, the uncertainties of \cmodel{} show larger 
    scatter for galaxies, which is expected given the diversity of galaxy shapes and sizes which adds complexity to the model-fitting process.
    At the same time, Figure \ref{fig:cmodel_mag} shows that the \cmodel{} algorithm in \hscpipe{} provides unbiased and consistent 
    photometry for galaxies across different bands and seeing conditions.

The typical $i$-band flux accuracy for \forced{} \cmodel{} is ${\sim}7-9$\% in the good-seeing \tract{} at $i_{\mathrm{Input}}<24.0$ mag. This moderately degrades to ${\sim}11$\% at $25.0$ mag. The performance is similar in the $i$-band bad-seeing \tract{}. At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the median magnitude offset
    between output and input values changes from \plus{}$0.041$ mag to
    \minus{}$0.005$ mag, which suggests that \forced{} \cmodel{} photometry is
    unbiased down to the very faint end.

    It is worth noting that the flux uncertainty from \synpipe{} are significantly 
    larger than the flux errors from \hscpipe{}, which does not take into account the 
    systematic uncertainties involved in the modeling fitting process. Even though our synthetic galaxy sample is  comprised of objects with simple single-\ser{} models, 
    \cmodel{} algorithm can only approximate them to a certain accuracy because of the background noise, deblending uncertainties, and priors imposed on model parameters. Given that real galaxies are more complex in structure, the uncertainties derived from our \synpipe{} tests should be treated as lower limits.

\alexie{What does this say about the values of SN from CMODEL then? If the unceratinties are underestimated, then the SN is overestimated? By how much? WOrth commenting on here?}

@@

    The accuracy of \forced{} \cmodel{} photometry is consistent across all filters.
    For the$g$, $r$, and $z$ bands, the photometric uncertainties are very similar to
    $i$-band results between $20.0$ and $25.0$ mag.
    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
    across the entire input magnitude range.
    The uncertainties for the $y$ band are slightly worse, ranging from 9\% to 17\% in the
    same magnitude bins.
    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
    the $y$ band at $>24.0$ mag. This bias in the $y$ band flux is equal to  \minus{}0.06 at $24.0$ mag to \minus{}0.22
    mag at 25.0 mag. Worse seeing conditions and a  higher background noise level mean that it is more
    difficult to detect faint objects in the $y$ band.
    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
    around the detection threshold.

Our synthetic galaxy sample is dominated by faint galaxies.  Hence, we have poor statistics for bright galaxies. However, we do find that at $i_{\mathrm{Input}}<20.0$, the \forced{} \cmodel{} photometry starts to systematically underestimate total fluxes. Based on external comparisons, the behavior of \cmodel{} for bright galaxies may 
    depend on galaxy types (e.g., \citealt{HSCDR1}).  Also, at bright magnitudes, another known issue is that the current \hscpipe{} (e.g., \hscpipe{} over-deblends around bright 
    objects. Inappropriately weight priors in \cmodel{}) may also lead to poorer photometric quality for bright galaxies.  Finally, at the imaging depth of HSC ($>29.0$\sb{} in the Wide Layer $i$ band),  \cmodel{} may simply not be a good choice for modeling bright 
    galaxies (e.g., for massive elliptical galaxies; see Huang\etal in prep.~for 
    more details).

We also find that highly blended galaxies tend to have systematically underestimated total 
    fluxes (with an average offset ${\sim}0.1$ mag) and larger photometric uncertainties in all five bands. However,  the contrast between relatively isolated and highly blended galaxies
    in photometric performance is not as stark as for synthetic
    stars (Fig \ref{fig:psf_mag}).

    We also test the \unforced{} \cmodel{} photometry in all five bands, and the
    results suggest similar accuracies.

    Fig \ref{fig:cmodel_diff} compared the difference between  \forced{} and \unforced{} \cmodel{} in $g$ and $y$.  We find that  \forced{} and \unforced{} \cmodel{} shows similar trends.  The main  noticeable trend is that galaxies brighter than $24.0$ mag in $g$ band, have systematically brighter \forced{} \cmodel{} magnitudes. This suggests that the \forced{} \cmodel{} is more accurate in the $g$ band.

>>>>

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Precision and Accuracy of the \cmodel{} magnitude}

    Fig \ref{fig:cmodel_mag} shows the precision and accuracy of \cmodel{} magnitude 
    in each band using the same format as Fig \ref{fig:psf_mag}.

    The overall performance of \cmodel{} photometry is reasonable down to 
    $i_{\mathrm{Input}}=25.2$ mag.
    Compared to the PSF photometry for stars, the statistical uncertainties of \cmodel{} 
    magnitudes are larger for galaxies, which is expected given the diversity of galaxy 
    shapes and sizes that adds complexity to the model-fitting process.
    At the same time, Figure \ref{fig:cmodel_mag} shows that the \cmodel{} algorithm in
    \hscpipe{} provides unbiased and consistent photometry for galaxies across 
    different bands and seeing conditions.

    The typical precision of $i$-band flux using \forced{} \cmodel{} is at 
    ${\sim}7-9$\% level in the \texttt{goodSeeing} \tract{} at 
    $i_{\mathrm{Input}}<24.0$ mag. 
    It moderately degrades to ${\sim}11$\% at $25.0$ mag. 
    The performance is similar in $i$ band for the \texttt{badSeeing} \tract{}. 
    At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the accuracies of \forced{} \cmodel{}
    magnitudes change from \plus{}$0.041$ mag to \minus{}$0.005$ mag, which suggest
    that \forced{} \cmodel{} photometry is unbiased down to the very faint end.

    It is worth noting that the flux uncertainty from \synpipe{} are significantly 
    larger than the flux errors from \hscpipe{}, which does not take into account the 
    systematic uncertainties involved in the modeling fitting process. 
    Even though our synthetic galaxy sample is comprised of objects with simple 
    single-\ser{} models, \cmodel{} algorithm can only approximate them to a certain 
    accuracy because of the background noise, deblending uncertainties, and priors 
    imposed on model parameters. 
    Given that real galaxies are more complex in structure, our quoted uncertainties 
    should be treated as lower limits.

@@

    The precision of \forced{} \cmodel{} photometry is consistent across all filters.
    For the $g$, $r$, and $z$ bands, the statistical uncertainties are very similar to
    $i$-band results between $20.0$ and $25.0$ mag.
    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
    across the entire input magnitude range.
    The precision for the $y$ band is slightly worse, ranging from 9\% to 17\% in the
    same magnitude bins.
    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
    the $y$ band at $>24.0$ mag. 
    This bias in the $y$ band flux is equal to \minus{}0.06 at $24.0$ mag to 
    \minus{}0.22 mag at 25.0 mag. 
    Worse seeing conditions and a higher background noise level mean that it is more
    difficult to detect faint objects in the $y$ band.
    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
    around the detection threshold.

    Our synthetic galaxy sample is dominated by faint galaxies 
    ($i_{\mathrm{Input}} > 24.0$ mag) that are crucial to key scientific goals of the 
    HSC survey.
    But it also means poor statistics for bright galaxies. 
    We do find that at $i_{\mathrm{Input}}<20.0$, the \forced{} \cmodel{} photometry 
    starts to systematically underestimate total fluxes. 
    Based on external comparisons, the behavior of \cmodel{} for bright galaxies may 
    depend on galaxy types (e.g., \citealt{HSCDR1}).  
    Also, at bright end, another known issue is that the current \hscpipe{}
    over-deblends around bright objects. 
    Inappropriately weight priors in \cmodel{} also leads to poorer photometric 
    quality for bright galaxies.  
    Finally, at the imaging depth of HSC ($>29.0$\sb{} in the Wide Layer $i$ band),  
    \cmodel{} may simply not be a good choice for modeling bright galaxies 
    (e.g., massive elliptical galaxies; see Huang\etal in prep.~for more details).

    We also find that highly blended galaxies tend to have systematically 
    underestimated total fluxes (with an average offset ${\sim}0.1$ mag) and 
    higher statistical uncertainties in all five bands. 
    However, the contrast between relatively isolated and highly blended galaxies
    in photometric performance is not as stark as for synthetic stars 
    (Fig \ref{fig:psf_mag}).

    We also test the \unforced{} \cmodel{} photometry in all five bands, and the
    results suggest similar precision.
    Fig \ref{fig:cmodel_diff} compares the difference between \forced{} and \unforced{} 
    \cmodel{} in $g$ and $y$ bands.  
    The main noticeable trend is that galaxies brighter than $24.0$ mag in the $g$ band 
    have systematically brighter \forced{} \cmodel{} magnitudes, which suggests that 
    the \forced{} \cmodel{} is more accurate in the $g$ band as the model parameters 
    are determined using band with higher \s2n{}.
